Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-01-22 doc_v2/doc_v2.Rmd
pdf

```{r wo120, fig.width = 8, fig.height=4.5, fig.cap="The figure on the left shows the actual Type I error while the figure on the right shows the Type II error for different validation window sizes and different chosen nominal alpha levels when the size of the optimization window = 120"}
wo120 <- errors %>% filter(wo==120)
wo120 %>% gather(type, error, actual:beta) %>%
  ggplot(aes(x = wv, y = error, colour = factor(alpha)))  + 
  geom_line() + geom_point() + facet_wrap(~type, scales="free") +
  theme_bw()+ 
  theme(legend.position="bottom")
```

@@

>>>>

```{r wo120, fig.width = 8, fig.height=4.5, fig.cap="The figure on the left shows the actual Type I error while the figure on the right shows the Type II error for different validation window sizes and different chosen nominal alpha levels when the size of the optimization window = 120"}
wo120 <- errors %>% filter(wo==120)
wo120 %>% gather(type, error, actual:beta) %>%
  ggplot(aes(x = wv, y = error, colour = factor(alpha)))  + 
  geom_line() + geom_point() + facet_wrap(~type, scales="free") +
  theme_bw()+ 
  theme(legend.position="bottom") +  ggtitle("Signatures" , subtitle = "Varying validation window sizes, Optimization window = 120")
```

@@

```{r wo120-profile, fig.width = 8, fig.height=4.5, fig.cap="The figure on the left shows the actual Type I error while the figure on the right shows the Type II error for different validation window sizes and different chosen nominal alpha levels when the size of the optimization window = 120"}
wo120_profile <- errors2 %>% filter(wo==120, coarse == 0.25) %>% 
  gather(type, error, actual:beta) %>% 
  ggplot(aes(x = wv, y = error, colour = factor(alpha)))  + 
  geom_line() + geom_point() + facet_wrap(~type, scales="free") +
    theme_bw()+ 
  theme(legend.position="bottom") + ggtitle("Profile" , subtitle = "Varying validation window sizes, Optimization window = 120, Coarseness = 0.25")

wo120_1<- wo120 %>% gather(type, error, actual:beta) %>%  
  ggplot(aes(x = wv, y = error, colour = factor(alpha)))+
  geom_line(linetype=5)+  geom_point(shape= 24) + facet_wrap(~type, scales="free") +
  theme_bw()+ 
  theme(legend.position="bottom") + ggtitle("Signatures" , subtitle = "Varying validation window sizes, Optimization window = 120")

wo120_profile
wo120_1
#multiplot(wo120_1, wo120_profile1)
```
